The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2017-02-06 manuscript/manuscript.Rnw
correct typos in annex evolutionary importance ¶

\subsubsection{Immune Regulation and Annexins}
The transcriptomes from multiple different species enabled us to
identify the set of expressed genes which are common to all placentas.
Components of the annexin complexes, including
\ac{ANXA2}, \ac{ANXA1}, \ac{S100A11}, and \ac{S100A10}
are expressed in all placentas examined, and argue for the evolution
importance of annexins in placenta function, where they likely
establish maternal-fetal
tolerance\cite{Liu.ea2015:AnnexinA2complexeswith,Hutchinson.ea2011:Molecularregulatorsofresolution,Aarli.ea1997:Suppressiveeffectonlymphoproliferation}.
We suggest that further research into molecular role of these annexin
complexes may illuminate how immune tolerance is maintained during
placentation because these appear to the the major class of immune
modulatory transcripts which are expressed in all placentas analyzed.

>>>>

\subsubsection{Immune Regulation and Annexins}
The transcriptomes from multiple different species enabled us to
identify the set of expressed genes which are common to all placentas.
Components of the annexin complexes, including
\ac{ANXA2}, \ac{ANXA1}, \ac{S100A11}, and \ac{S100A10}
are expressed in all placentas examined, and argue for the evolutionary
importance of annexins in placenta function, where they likely
establish maternal-fetal
tolerance\cite{Liu.ea2015:AnnexinA2complexeswith,Hutchinson.ea2011:Molecularregulatorsofresolution,Aarli.ea1997:Suppressiveeffectonlymphoproliferation}.
We suggest that further research into the molecular role of these annexin
complexes may illuminate how immune tolerance is maintained during
placentation, because annexins appear to be the major class of immune
modulatory transcripts which are expressed in all placentas analyzed.
